Fixing Vulnerabilities Potentially Hinders Maintainability

### 2020-05-27 paper/icsme20.tex
small fixes

 \begin{figure}[htp]
     \begin{adjustwidth}{-2.5cm}{-1cm}  
  	\centering
  	\includegraphics[width=0.51\textwidth]{figures/main_per_guideline.pdf}
  	\caption{Impact of the security patches per guideline.}
 	\label{fig:guidelines}
    \end{adjustwidth}	
	\vspace{-0.5cm}
 \end{figure}

@@

This section presents the implications that we retrieved from this
study and think are important to consider in the future by developers.
Our results exhibit evidence that developers may have to
reduce maintainability for the sake of security. We understand that developers
should be able to patch and produce secure code without hindering the maintainability of
their projects. But there are still some concerns that need to be addressed
and that this study tries to bring awareness for:

\begin{itemize}

	\item\textbf{Tools for Patch Risk Detection:}
	Design debt of one guideline can lead
	to severe impacts on the software quality~\cite{10.1145/1985362.1985366}. 
	Thus, tools like Better Code Hub and static analysis (e.g., SonarQube, Codacy,
	ESLint, Infer, and more) should be leveraged to 
	assess the risk of patching vulnerabilities - alongside pull
	requests/code reviews. While static code analysis
	may be daunting due to the number of rules and different effects
	on maintainability, BCH uses the top-$10$ of the guidelines
	with the highest effect on maintainability. Yet, static analysis 
	can be used to complement the source code analysis, introduce
	the capability of vulnerability detection, and, predict and
	reduce the risk of hindering maintainability.

	\item\textbf{Computer Curricula Needs to be Updated:}
	Software Developers lack the knowledge to create secure and
	maintainable code. Mainly because academic curricula is not yet prepared
	to properly educate them. Universities should do their part on making
	this possible. Online services such as BCH have a great potential to help
	developers to be more aware of the maintainability issues introduced by their
	changes. Thus, developers can 
	put more work into improving their code maintainability and avoiding the risk
	of introducing new vulnerabilities while patching older ones.

	\item\textbf{Secure Programming Languages Wanted:} Programming Languages 
	should provide new design patterns to easily implement security weaknesses 
	without endangering maintainability.
	Ultimately, new programming languages, both secure and maintainable by design,
	may be designed to help developers be highly productive when writing and
	maintaining secure applications. One example is the need for designing new
	authorization mechanisms since these are one of the most complex security
	features to implement.

	\item\textbf{Poor Coding Practices Documentation:} 
	Software documentation must provided to developers with the
	best practices to implement secure and maintainable software. Unmaintainable
	code is difficult to test, analyze and re-use. Software companies must
	do an effort to provide these artifacts to their developers, in order,
	to avoid the introduction of new vulnerabilities while patching older ones.

\end{itemize}

>>>>

 \begin{figure}[htp]
 	\vspace{-0.9cm}

     \begin{adjustwidth}{-2.5cm}{-1cm}  
  	\centering
  	\includegraphics[width=0.51\textwidth]{figures/main_per_guideline.pdf}

    \end{adjustwidth}
  	\caption{Impact of the security patches per guideline. For each guideline, $3$ types of impact in the software maintainability are presented: negative, maintainability decreases (red); none, maintainability remains the same (yellow); and, positive, maintainability increases (green).}
 	\label{fig:guidelines}	
	\vspace{-0.5cm}
 \end{figure}

@@

This section presents the implications that we retrieved from this
study and think are important to consider in the future by developers.
Our results exhibit evidence that developers may have to
reduce maintainability for the sake of security. We understand that developers
should be able to patch and produce secure code without hindering the maintainability of
their projects. But there are still some concerns that need to be addressed
and that this study tries to bring awareness for:
%
\\\textit{\textbf{Tools for Patch Risk Detection:}}
	Design debt of one guideline can lead
	to severe impacts on the software quality~\cite{10.1145/1985362.1985366}. 
	Thus, tools like Better Code Hub and static analysis (e.g., SonarQube, Codacy,
	ESLint, Infer, and more) should be leveraged to 
	assess the risk of patching vulnerabilities - alongside pull
	requests/code reviews. While static code analysis
	may be daunting due to the number of rules and different effects
	on maintainability, BCH uses the top-$10$ of the guidelines
	with the highest effect on maintainability. Yet, static analysis 
	can be used to complement the source code analysis, introduce
	the capability of vulnerability detection, and, predict and
	reduce the risk of hindering maintainability.
%
\\\textit{\textbf{Computer Curricula Needs to be Updated:}}
	Software Developers lack the knowledge to create secure and
	maintainable code. Mainly because academic curricula is not yet prepared
	to properly educate them. Universities should do their part on making
	this possible. Online services such as BCH have a great potential to help
	developers to be more aware of the maintainability issues introduced by their
	changes. Thus, developers can 
	put more work into improving their code maintainability and avoiding the risk
	of introducing new vulnerabilities while patching older ones.
%	
\\\textit{\textbf{Secure Programming Languages Wanted:}} Programming Languages 
	should provide new design patterns to easily implement security weaknesses 
	without endangering maintainability.
	Ultimately, new programming languages, both secure and maintainable by design,
	may be designed to help developers be highly productive when writing and
	maintaining secure applications. One example is the need for designing new
	authorization mechanisms since these are one of the most complex security
	features to implement.
%
\\\textit{\textbf{Poor Coding Practices Documentation:}}
	Software documentation must provided to developers with the
	best practices to implement secure and maintainable software. Unmaintainable
	code is difficult to test, analyze and re-use. Software companies must
	do an effort to provide these artifacts to their developers, in order,
	to avoid the introduction of new vulnerabilities while patching older ones.
